---
title: "Conclusion"
author: "Elodie Kwan and Katia Voltz"
output: html_document
date: '2022-05-20'
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
source(here::here("scripts/setup.R"))
```

```{r echo=FALSE}
options(knitr.duplicate.label = 'allow')
```

## Conclusion

Recall, we computed several models. We first started with three versions of the classification tree, then we performed two logistic regression, two nearest neighbor, four support vector machines, one neural network and one gradient boosting model. Through all these models we noticed a common point which was their poor ability to predict the "Bad credit" cases. Knowing the purpose of this report, it is not really good as the banker might then misjudge the new applicant and refuse to give a credit while the applicant might be a good one. This will result in an opportunity loss for our client, the banker. 

Since several models has been performed throughout this analysis, we came up with the conclusion that there might be a bias in the data itself. Indeed we might have good information and knowledge on the characteristics of a "good" applicant but the data could be improved and include more information on the "bad" applicant. This way, the models will then be able to be better trained. 

### Our recommendations/Suggestions 
As we saw the models could be improved as the accuracies are not going over the 70%. We think that others variables describing better the 'Bad' credits could be added. For example, it would be interesting to know whether the applicant is under litigation for not paying back someone ('acte de poursuite' in French).

## References 



## Annexes 

#### Appendix A : Definitions of the attributes of the German Credit dataset 

+ 1) OBS# : Observation No. 
+ 2) CHK_ACCT : Checking account status 
  + 0 : < 0 DM 
  + 1 : 0 < · · · < 200 DM
  + 2 : >= 200 DM
  + 3 : no checking account
+ 3) DURATION : Duration of credit in months
+ 4) HISTORY : Credit history
  + 0 : no credits taken
  + 1 : all credits at this bank paid back duly
  + 2 : existing credits paid back duly till now
  + 3 : delay in paying off in the past
  + 4 : critical account
+ 5) NEW_CAR : Purpose of credit 
  + car (new) 0 : No, 1 : Yes
+ 6) USED_CAR : Purpose of credit 
  + car (used) 0 : No, 1 : Yes
+ 7) FURNITURE : Purpose of credit 
  + furniture/equipment 0 : No, 1 : Yes
+ 8) RADIO/TV : Purpose of credit 
  + radio/television 0 : No, 1 : Yes
+ 9) EDUCATION Purpose of credit 
  + education 0 : No, 1 : Yes
+ 10) RETRAINING Purpose of credit 
  + retraining 0 : No, 1 : Yes
+ 11) AMOUNT : Credit amount
+ 12) SAV_ACCT : Average balance in savings account 
  + 0 : < 100 DM
  + 1 : 100 <=· · · < 500 DM
  + 2 : 500 <= · · · < 1000 DM
  + 3 : >= 1000 DM
  + 4 : unknown/no savings account
+ 13) EMPLOYMENT : Present employment since 
  + 0 : unemployed
  + 1 : < 1 year
  + 2 : 1 <= · · · < 4 years
  + 3 : 4 <= · · · < 7 years
  + 4 : >= 7 years
+ 14) INSTALL_RATE : Installment rate as % of disposable income
+ 15) MALE_DIV : Applicant is male and divorced 
  + 0 : No, 1 : Yes
+ 16) MALE_SINGLE : Applicant is male and single 
  + 0 : No, 1 : Yes
+ 17) MALE_MAR_WID : Applicant is male and married or a widower
  + 0 : No, 1 : Yes
+ 18) CO-APPLICANT : Application has a co-applicant 
  + 0 : No, 1 : Yes
+ 19) GUARANTOR : Applicant has a guarantor 
  + 0 : No, 1 : Yes
+ 20) PRESENT_RESIDENT : Present resident since - years 
  + 0 : <= 1 year
  + 1 : 1 < · · · <= 2 years
  + 2 : 2 < · · · <= 3 years
  + 3 :> 4 years
+ 21) REAL_ESTATE : Applicant owns real estate
  + 0 : No, 1 : Yes
+ 22) PROP_UNKN_NONE : Applicant owns no property (or unknown)
  + 0 : No, 1 : Yes
+ 23) AGE : Age in years 
+ 24) OTHER_INSTALL : Applicant has other installment plan credit
  + 0 : No, 1 : Yes
+ 25) RENT : Applicant rents 
  + 0 : No, 1 : Yes
+ 26) OWN_RES : Applicant owns residence 
  + 0 : No, 1 : Yes
+ 27) NUM_CREDITS : Number of existing credits at this bank
+ 28)  JOB : Nature of job 
  + 0 : unemployed/unskilled non-resident
  + 1 : unskilled - resident
  + 2 : skilled employee/official
  + 3 : management/self-employed/
  + highly qualified employee/officer
+ 29) NUM_DEPENDENTS : Number of people for whom liable to provide maintenance
+ 30) TELEPHONE : Applicant has phone in his or her name
  + 0 : No, 1 : Yes
+ 31) FOREIGN + Foreign worker 
  + 0 : No, 1 : Yes



#### Appendix B : Barplots of the categorical variables from the EDA part. 

<br> 

```{r pick_reuse, ref.label=c('chunck_reuse1','chunck_reuse2','chunck_reuse3', 'chunck_reuse4'), include=FALSE}

```

<br>

```{r pick_annex_1, ref.label='chunk_annex_1', fig.show="hold", out.width="50%", echo = FALSE}

```

#### Appendix C : General summary of the German Credit dataset

```{r pick_annex_2, ref.label='chunk_annex_2', fig.show="hold", out.width="50%", echo = FALSE}

```




