---
title: "Exploratory Data Analysis"
author: "Elodie Kwan and Katia Voltz"
date: '2022-04-26'
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r echo=FALSE}
source(here::here("scripts/setup.R"))
```

In this section, we will proceed to an exploratory data analysis of the **German Credit data**. 

Let's start by importing the dataset. 
```{r}
German_credit <- read.csv("./../Data_DA/GermanCredit.csv", header = TRUE, sep = ";")
```


## Get to know the data 

### Title : german credit data 
### Name of the file : GermanCredit.cvs
### Abstract
The German Credit data has data on 1000 past credit applicants, described by 30 variables. Each applicant is rated as "Good" or "Bad" credit (encoded as 1 and 0 respectively in the response variable). 


**Goal** : We want to obtain a model that may be used to determine if new applicants present a good or bad credit risk

+ Number of instances : 1000
+ Number of attributes : 30
+ Attribute Information :

```{r}
str(German_credit)

summary(German_credit)
```

We notice that the variable **EDUCATION** has a minimum value of '-1' but it should be '0' since there are only 2 levels (0 and 1). Indeed, the observation 37 indicate a value of '-1' for **EDUCATION**. 
We notice another strange value, in the variable **GUARANTOR**, the maximum value is of '2' while it does not mean anything in our data set. 

After discussion with the Banker, he gave us the correct values to these 2 mistakes. Observation 37 of **EDUCATION** and observation 234 of **GUARANTOR** should be equal to 1.

```{r}
German_credit$EDUCATION[37] <- 1
German_credit$EDUCATION <- as.factor(German_credit$EDUCATION)

German_credit$GUARANTOR[234] <- 1
German_credit$GUARANTOR <- as.factor(German_credit$GUARANTOR)
```


We see that the variable **AGE** has a maximum of 125. This is strange because it is very unlikely that someone lives to the age of 125. We talked to the banker and he confirmed our doubts by telling us that a mistake has been made. At the observation 537, the correct age of the client is 75 years old. He asks us to correct this value in our data set. 

```{r}
German_credit$AGE[537] <- 75
```


+ There are no missing values.
 
```{r}
which(is.na(German_credit))
```

+ The response variable is the '**Response**' variable - last column on the data. 
 
Response variable : credit rating is good
 
1. 0 : No

2. 1 : Yes


We have to make sure that the class of the variables are correct. As described above, all the variables are defined as *integer* but we know that we should have numerical and categorical variables in our dataset. Therefore, we have to transform the class of some of them.

```{r}
German_credit$DURATION <- as.numeric(German_credit$DURATION)
German_credit$AMOUNT <- as.numeric(German_credit$AMOUNT)
German_credit$INSTALL_RATE <- as.numeric(German_credit$INSTALL_RATE)
German_credit$AGE <- as.numeric(German_credit$AGE)
German_credit$NUM_CREDITS <- as.numeric(German_credit$NUM_CREDITS)
German_credit$NUM_DEPENDENTS <- as.numeric(German_credit$NUM_DEPENDENTS)

for (i in 1:ncol(German_credit)){
  if (class(German_credit[,i])=="integer"){
    German_credit[,i] <- factor(German_credit[,i])
    }
}

str(German_credit)
```

The binomial data are set as factors and the others as numerical. 


We can now describe the variables one more time and we should get better results.  

```{r}
describe(German_credit)
introduce(German_credit)

plot_intro(German_credit)
```

The plot helps us to see the percentage of continuous variable, the percentage of discrete variables and whether or not some observations are missing. 


## Visualization of the data 
First, we plot all the continuous variables into histograms and their corresponding density plots. 

```{r}
plot_histogram(German_credit)
plot_density(German_credit)
```

Our first notice is that the data are not really normally distributed. Some of them are right-tailed.

We can look at the tails and outliers more carefully through boxplots. 

```{r}
plot_boxplot(German_credit, by = 'RESPONSE',  ncol = 2,
             title = "Side-by-side boxplots")
```

This seems not to be disturbing. It makes sense that only a few people has a big credit amount. However it seems that the 'bad' clients tends to ask for bigger credit amount than 'good' clients. 

Now, we can make some barplots of the categorical variables.

```{r}
for (i in 1:ncol(German_credit)){
  if (class(German_credit[,i])=="factor"){
    print(ggplot(German_credit) +
            geom_bar(aes(x=German_credit[,i]), fill = "coral") +
            ggtitle(paste("Barplot of", colnames(German_credit)[i])) +
            labs(x = paste(colnames(German_credit)[i])))
}}

```


From those barplots we can see: 

+ The majority of people do not check their account status. (CHK_ACCT)
+ Most people have an average balance of less than < 100 DM in their saving account. (SAV_ACCT)
+ Most of the applicants has its own residence. (OWN_RES)
+ Almost none of the applicants is a foreign worker. (FOREIGN) 
+ We have more information on people that are 'good' applicants and less information on 'bad' applicants. It would be better to have more information on 'bad' applicants as well in order to make good predictions with models. We will have to take this into account later. (RESPONSE)

A general summary can be done. 

```{r}
dfSummary(German_credit, style = 'grid')
```


### Correlation plot : 

Correlation plot between continuous variables : 
```{r}
plot_correlation(German_credit, type= 'c', cor_args = list( 'use' = 'complete.obs'))
```

There are little correlation between the continuous variables. We can notice that there is a correlation of 62% between the variable **DURATION** and **AMOOUNT**. This makes sense and is known by the bankers that the bigger the amount of credit, the longer the duration of the credit in months will last. 

Correlation plot between categorical variables : 
```{r}
plot_correlation(German_credit, type= 'd')
```

It is difficult to look at the correlation since there are a lot of variables on the graph. 
We can still see higher correlation between **RESPONSE 1**: 

+ and people that do not check their account (CHK_ACCT_3) 
+ and people that have a critical historical account (HISTORY_4)
+ and the variable _REAL_ESTATE_ (REAL_ESTATE)
+ and applicant that does not have their own property (PROP_UNKN_NONE_0)
+ and applicant that have their own residence (OWN_RES_1)

We can also see some correlation between **RESPONSE 0**: 

+ and people that have a checking account status < 0 DM (CHK_ACCT_0)
+ and people that have an average balance in savings account < 100 DM (SAV_ACCT_0)
+ and the variable _REAL_ESTATE_ (REAL_ESTATE)

### PCA Exploration:
It is good to perform a PCA Exploration in order to reduce the dimensions or/and see which variables to select. 

We start by selecting the numerical values:

```{r}
German_credit.num <- German_credit %>% 
  select('DURATION', 'AMOUNT', 'INSTALL_RATE', 'AGE', 'NUM_CREDITS','NUM_DEPENDENTS')
```

```{r}
German_credit.pca <- prcomp(German_credit.num, center = TRUE, scale = TRUE)
summary(German_credit.pca)
```

From the PCA summary we can see 4 principal components should be taken into account in order to explain approximately 81% of the variation of the data.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(FactoMineR)
resultats_pca <- PCA(German_credit.num, scale.unit = TRUE, ncp = 5, graph = FALSE)
```

#### Eigenvalue analysis:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
eig.val <- get_eigenvalue(resultats_pca)
eig.val
```
Need to choose 3 dimensions according to eigenvalues. Dim1/2/3 > 1

```{r, echo = FALSE, message = FALSE, warning = FALSE, out.width = "100%", fig.align="center"}
fviz_eig(resultats_pca, addlabels = TRUE)
```


```{r}
fviz_pca_ind(German_credit.pca,
             col.ind = "cos2", # Colorer par le cos2
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     
             )

```

```{r}
fviz_pca_var(German_credit.pca,
             col.var = "contrib", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     
             )

```

From this circle of correlations, we see that : 

+ The first principal component PC1 is strongly positively correlated with the variables **AMOUNT** and **DURATION**. So the larger PC1, the larger these features. It is also a little bit negatively correlated with **INSTALL_RATE**.  
+ The second principal component PC2 is strongly positively correlated with **AGE**, **NUM_DEPENDENTS** and **NUM_CREDITS**. 


From this biplot, we can see some characteristics of the observations.

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.width=9,fig.height=7, out.width = "120%", fig.align="center"}
fviz_pca_biplot(resultats_pca, repel = TRUE,
                col.var = "blue", # Couleur des variables
                habillage= German_credit$RESPONSE)
```
Here, we can see the distribution of the response variables (0-1) according to the reduced dimension. What we can observe, is that the Bad credits: 0, look a little bit more positively correlated ot dimension 1. Therefore, more correlated to Amount and Duration. 
Compared to Good Credits, it looks positively correlated to dimesion 2; AGE, Num_Credits, Num_dependents.



We can export the dataset as we have made some modifications. It will be easier for the other files. 

```{r}
# write.csv(German_credit,"./../Data_DA/GermanCredit_cleaned.csv", row.names = FALSE)
```
